---
title: "Binder Example"
output: html_notebook
---

This is an example of using `binder` with the {holepunch} package for `R`

```{r}
library(holepunch)
library(usethis)
```

The code below creates a `DESCRIPTION` file which, among other things, lists the R packages that are dependencies of this project (this is the same mechanism used by R packages to specify their dependencies). 

By default the `DESCRIPTION` file is populated with the any packages that {holepunch} can find as being used in this project.

```{r}
write_compendium_description(
	package = "Testing {holepunch} Dockerfile generation for R", 
	description = "holepunch test ... "
)
```

Checkout the contents of the `DESCRIPTION` file, you'll notice some placeholder text that you may wish to replace with the actual information about your project.

instructions on initialisng the git repo and pushing ot github

```{bash}
git init
git add -A
git commit -am"init"
git remote add git@github.com:RichardJActon/holepunch_binder_example.git # ssh auth
```

```{r}
write_dockerfile(maintainer = "Richard J. Acton") 
```

Pick a license under which you wish to share your code.
Any code you make public should ideally be associated with a license so that others know how they can use your work.
I'm using the GPLv3 license for this project which means all derivative of this must be licensed the same way, a popular more permissive license is the MIT with this people can use your code in differently licensed projects.
The {usethis} package has a number of helper functions to make this easy.
You will note if you take a look at the `DESCRIPTION` file that the license is updated there as well as a copy of the license being written to `LICENSE.md`

```{r}
usethis::use_gpl3_license()
```

{usethis} also has helper functions for things like adding package dependencies.
let's use {usethis} to add {usethis} as a dependency for this project.

```{r}
usethis::use_package("usethis")
```

Create a README.md file for the project to contain a description of it that will live on your repository's home page on github

```{r}
usethis::use_readme_md()
```

Add the Launch Rstudio binder badge to the README file so that people visitng your repo can launch your project in a container

```{r}
generate_badge()
```

```{r}
build_binder()
```

# References

see: https://github.com/karthik/holepunch
