---
title: "Binder Example"
output: html_notebook
---

This is an example of using `binder` with the {holepunch} package for `R`

```{r}
library(holepunch)
```

The code below creates a `DESCRIPTION` file which, among other things, lists the R packages that are dependencies of this project (this is the same mechanism used by R packages to specify their dependencies). 

By default the `DESCRIPTION` file is populated with the any packages that {holepunch} can find as being used in this project.

```{r}
write_compendium_description(
	package = "Testing {holepunch} Dockerfile generation for R", 
	description = "holepunch test ... "
)
```

Checkout the contents of the `DESCRIPTION` file, you'll notice some placeholder text that you may wish to replace with the actual information about your project.

```{r}
git2r::init()
git2r::remote_add(
	name = "holepunch_binder_example",
	url = "git@github.com:/RichardJActon/holepunch_binder_example.git"
)
git2r::add(path = "*")
git2r::commit(message = "init")
#git2r::branch_set_upstream(branch =  git2r::branches()$master, "master")
git2r::push(
	refspec = "refs/heads/master",
	name = "holepunch_binder_example", set_upstream = TRUE,
	credentials = git2r::cred_ssh_key(passphrase = getPass::getPass())
)
```


```{r}
write_dockerfile(maintainer = "Richard J. Acton") 
```

```{r}
generate_badge()
```

```{r}
build_binder()
```

